|

### 2021-03-10 supplementary_information_science.Rmd
edits: si, minor correction
Update supplementary_information_science.Rmd

where $E(\cdot)$ is a known function (e.g., exponential), $u$ the input of interest (a value for the explanatory variable of interest), $v$ all the other inputs (a vector in general), $\Theta$ a set of parameters in a regression model. In general, $\delta_u$ depends on $u^{(1)}$ and $u^{(2)}$ (the beginning and end points of the hypothesized change in the explanatory variable of interest), $v$, and $\Theta$. Therefore, Gelman and Pardoe [@gelmanAveragePredictiveComparisons2007] defined the *average predictive comparison* $\Delta_u$, the mean value of $\delta_u$ over specified distributions of the inputs and model parameters:

@@

which should represent how likely it is for $u$ to transition from $u_i$ to $u_j$ with $v_i$ (note that $v_i$ is in general a vector of explanatory variables for data point $i$). We used the following weighting function based on Mahalanobis distances following Gelman and Pardoe [@gelmanAveragePredictiveComparisons2007]:

@@

\begin{equation}
  S.E.(\hat \Delta_{u,s}) = \sqrt{\frac{1}{S-1} \sum_{s-1}^S (\hat \Delta_{u,s} - \hat \Delta_{u})^2}
\end{equation}

>>>>

where $E(\cdot)$ is a known function (e.g., exponential), $u$ the input of interest (a value for the explanatory variable of interest), $v$ all the other inputs (a vector in general), $\Theta$ a set of parameters in a regression model. In general, $\delta_u$ depends on $u^{(1)}$ and $u^{(2)}$ (the lower and higher points of the hypothesized change in the explanatory variable of interest), $v$, and $\Theta$. Therefore, Gelman and Pardoe [@gelmanAveragePredictiveComparisons2007] defined the *average predictive comparison* $\Delta_u$, the mean value of $\delta_u$ over specified distributions of the inputs and model parameters:

@@

which should represent the likelihood of $u$ changing from $u_i$ to $u_j$ with $v_i$ (note that $v_i$ is in general a vector of explanatory variables for data point $i$). We used the following weighting function based on Mahalanobis distances following Gelman and Pardoe [@gelmanAveragePredictiveComparisons2007]:

@@

\begin{equation}
  S.E.(\hat \Delta_{u,s}) = \sqrt{\frac{1}{S-1} \sum_{s=1}^S (\hat \Delta_{u,s} - \hat \Delta_{u})^2}
\end{equation}
